Upper Limits on CN from Falling Evaporating Bodies\\seen towards \bp{}

### 2024-09-06 src/tex/ms.tex
added CN_ACF plot

Note that for HARPS, the change of fiber in \textcolor{red}{June 2015 (JD$\sim$2457180)} resulted in an overall change of the blaze profile, and therefore, the spectra before and after this date were separately post-processed as outlined below in the Sect.~/ref{sect:starcor}.

@@

@@

This master CCF is then fitted in the same way as the nightly CCFs, and the uncertainties on the parameters is taken directly from curve\_fit assuming no covariance between the parameters. The final detection significance for the injected models is determined by the amplitude divided by its uncertainty, and shown in \hl{Figure} for the circumstellar gas and in \hl{Figure} for the strongest exocomet features.

>>>>

Note that for HARPS, the change of fiber in June 2015 (JD$\sim$2,457,180) resulted in an overall change of the blaze profile, and therefore, the spectra before and after this date were separately post-processed as outlined below in the Sect.~/ref{sect:starcor}.

@@

\begin{figure}
    \begin{centering}
        \includegraphics[width=\columnwidth]{figures/CN_ACF.pdf}
        \caption{CN autocorrelation function for different temperatures.}
        \label{fig:CN_ACF}
        \script{plot_CN_ACF.py}
    \end{centering}
\end{figure}

@@

This master CCF is then fitted in the same way as the nightly CCFs, and the uncertainties on the parameters is taken directly from curve\_fit assuming no covariance between the parameters. The final detection significance for the injected models is determined by the amplitude divided by its uncertainty, and shown in Figure~\ref{fig:CN_stellar_frame} for the circumstellar gas and in Figure~\ref{fig:CN_exocomet_frame} for the strongest exocomet features.
